\subsection{GPU Software}
    GPU software encompasses various tools and frameworks that facilitate the development and execution of parallel programs on GPUs. Major components include:

\begin{itemize}
    \item \textbf{CUDA:} NVIDIA’s Compute Unified Device Architecture (CUDA) is a parallel computing platform and API that allows developers to leverage NVIDIA GPUs for general-purpose computing. CUDA provides extensions to standard programming languages such as C, C++, and Fortran, and includes a comprehensive toolkit for developing GPU-accelerated applications. It supports features like kernel programming, memory management, and inter-thread synchronization.
    \item \textbf{OpenCL:} The Open Computing Language (OpenCL) is an open standard for parallel programming across heterogeneous systems, including GPUs from various vendors. OpenCL provides a unified programming model and API that enables developers to write code that can run on different types of processors (CPUs, GPUs, FPGAs) and is suitable for a wide range of applications.
    \item \textbf{Libraries and Frameworks:} Several libraries and frameworks provide pre-built functions and abstractions for GPU programming, making it easier to develop high-performance applications:
    \begin{enumerate}
        \item \textbf{cuBLAS:} A library for performing basic linear algebra operations on NVIDIA GPUs, optimized for performance.
        \item \textbf{cuDNN:} A library for deep neural network operations, providing highly optimized routines for deep learning tasks.
        \item \textbf{TensorFlow and PyTorch:} Popular machine learning frameworks that utilize GPU acceleration to improve training and inference performance.
    \end{enumerate}
    \item \textbf{Driver Software:} GPU drivers are essential for enabling communication between the operating system and GPU hardware. They handle the execution of GPU-accelerated applications, manage resources, and provide support for various APIs and frameworks. Regular updates to drivers ensure compatibility with new software and hardware features.
    \item \textbf{Development Tools:} Various development tools and IDEs (Integrated Development Environments) support GPU programming by providing debugging, profiling, and performance analysis capabilities. Examples include NVIDIA Nsight and AMD ROCm tools.
\end{itemize}
    
    Understanding these software components and their interaction with GPU hardware is crucial for developing efficient GPU-accelerated applications and achieving optimal performance.
